Paper 1: Vitis

### 2018-02-21 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
ac_tba_glm <- glm(leaf~teeth.blade.area, data = ac_all, family = gaussian())
summary(ac_tba_glm)
plot(ac_tba_glm)
beep(sound = 3, expr = NULL)
```

@@

>>>>

```{r}
ac_tba_glm <- glm(leaf~teeth.blade.area, data = ac_all, family = gaussian())
summary(ac_tba_glm)
plot(ac_tba_glm)
```

@@

We ran a GLM for leaf number and all variables. 
```{r}
ac_all_glm <- glm(leaf~total.teeth + feret.diameter.ratio + tooth.area.perimeter + tooth.area.int.perimeter + average.tooth.area + tooth.area.blade.area + teeth.perimeter + teeth.int.perimeter + perimeter.area + perimeter.ratio + compactness + shape.factor + teeth.blade.area, data = ac_all, family = gaussian())
summary(ac_all_glm)
plot(ac_all_glm)
```

We tested *Vitis aestivalis*.

```{r}
skim(av_all)
av_tt_glm <- glm(leaf~total.teeth, data = av_all, family = gaussian())
summary(av_tt_glm)
plot(av_tt_glm)
```

```{r}
av_fdr_glm <- glm(leaf~feret.diameter.ratio, data = av_all, family = gaussian())
summary(av_fdr_glm)
plot(av_fdr_glm)
```

```{r}
av_tap_glm <- glm(leaf~tooth.area.perimeter, data = av_all, family = gaussian())
summary(av_tap_glm)
plot(av_tap_glm)
```

```{r}
av_taip_glm <- glm(leaf~tooth.area.int.perimeter, data = av_all, family = gaussian())
summary(av_taip_glm)
plot(av_taip_glm)
```

```{r}
av_ata_glm <- glm(leaf~average.tooth.area, data = av_all, family = gaussian())
summary(av_ata_glm)
plot(av_ata_glm)
```

```{r}
av_taba_glm <- glm(leaf~tooth.area.blade.area, data = av_all, family = gaussian())
summary(av_taba_glm)
plot(av_taba_glm)
```

```{r}
av_tp_glm <- glm(leaf~teeth.perimeter, data = av_all, family = gaussian())
summary(av_tp_glm)
plot(av_tp_glm)
```

```{r}
av_tip_glm <- glm(leaf~teeth.int.perimeter, data = av_all, family = gaussian())
summary(av_tip_glm)
plot(av_tip_glm)
```

```{r}
av_pa_glm <- glm(leaf~perimeter.area, data = av_all, family = gaussian())
summary(av_pa_glm)
plot(av_pa_glm)
```

```{r}
av_pr_glm <- glm(leaf~perimeter.ratio, data = av_all, family = gaussian())
summary(av_pr_glm)
plot(av_pr_glm)
```

```{r}
av_cp_glm <- glm(leaf~compactness, data = av_all, family = gaussian())
summary(av_cp_glm)
plot(av_cp_glm)
```

```{r}
av_sf_glm <- glm(leaf~shape.factor, data = av_all, family = gaussian())
summary(av_sf_glm)
plot(av_sf_glm)
```

```{r}
av_tba_glm <- glm(leaf~teeth.blade.area, data = av_all, family = gaussian())
summary(av_tba_glm)
plot(av_tba_glm)
```

We ran a GLM for leaf number and multiple variables. 
```{r}
av_clim_glm <- glm(leaf~feret.diameter.ratio + tooth.area.blade.area + teeth.blade.area + teeth.int.perimeter, data = av_all, family = gaussian())
summary(av_clim_glm)
plot(av_clim_glm)
```

We ran a GLM for leaf number and all variables. 
```{r}
av_all_glm <- glm(leaf~total.teeth + feret.diameter.ratio + tooth.area.perimeter + tooth.area.int.perimeter + average.tooth.area + tooth.area.blade.area + teeth.perimeter + teeth.int.perimeter + perimeter.area + perimeter.ratio + compactness + shape.factor + teeth.blade.area, data = av_all, family = gaussian())
summary(av_all_glm)
plot(av_all_glm)
```

we tested *Vitis amurensis*.

```{r}
skim(am_all)
am_tt_glm <- glm(leaf~total.teeth, data = am_all, family = gaussian())
summary(am_tt_glm)
plot(am_tt_glm)
```

```{r}
am_fdr_glm <- glm(leaf~feret.diameter.ratio, data = am_all, family = gaussian())
summary(am_fdr_glm)
plot(am_fdr_glm)
```

```{r}
am_tap_glm <- glm(leaf~tooth.area.perimeter, data = am_all, family = gaussian())
summary(am_tap_glm)
plot(am_tap_glm)
```

```{r}
am_taip_glm <- glm(leaf~tooth.area.int.perimeter, data = am_all, family = gaussian())
summary(am_taip_glm)
plot(am_taip_glm)
```

```{r}
am_ata_glm <- glm(leaf~average.tooth.area, data = am_all, family = gaussian())
summary(am_ata_glm)
plot(am_ata_glm)
```

```{r}
am_taba_glm <- glm(leaf~tooth.area.blade.area, data = am_all, family = gaussian())
summary(am_taba_glm)
plot(am_taba_glm)
```

```{r}
am_tp_glm <- glm(leaf~teeth.perimeter, data = am_all, family = gaussian())
summary(am_tp_glm)
plot(am_tp_glm)
```

```{r}
am_tip_glm <- glm(leaf~teeth.int.perimeter, data = am_all, family = gaussian())
summary(am_tip_glm)
plot(am_tip_glm)
```

```{r}
am_pa_glm <- glm(leaf~perimeter.area, data = am_all, family = gaussian())
summary(am_pa_glm)
plot(am_pa_glm)
```

```{r}
am_pr_glm <- glm(leaf~perimeter.ratio, data = am_all, family = gaussian())
summary(am_pr_glm)
plot(am_pr_glm)
```

```{r}
am_cp_glm <- glm(leaf~compactness, data = am_all, family = gaussian())
summary(am_cp_glm)
plot(am_cp_glm)
```

```{r}
am_sf_glm <- glm(leaf~shape.factor, data = am_all, family = gaussian())
summary(am_sf_glm)
plot(am_sf_glm)
```

```{r}
am_tba_glm <- glm(leaf~teeth.blade.area, data = am_all, family = gaussian())
summary(am_tba_glm)
plot(am_tba_glm)
```

We ran a GLM for leaf number and multiple variables. 
```{r}
am_clim_glm <- glm(leaf~feret.diameter.ratio + tooth.area.blade.area + teeth.blade.area + teeth.int.perimeter, data = am_all, family = gaussian())
summary(am_clim_glm)
plot(am_clim_glm)
```

We ran a GLM for leaf number and all variables. 
```{r}
am_all_glm <- glm(leaf~total.teeth + feret.diameter.ratio + tooth.area.perimeter + tooth.area.int.perimeter + average.tooth.area + tooth.area.blade.area + teeth.perimeter + teeth.int.perimeter + perimeter.area + perimeter.ratio + compactness + shape.factor + teeth.blade.area, data = am_all, family = gaussian())
summary(am_all_glm)
plot(am_all_glm)
```

We tested *Vitis riparia*.

```{r}
skim(r_all)
r_tt_glm <- glm(leaf~total.teeth, data = r_all, family = gaussian())
summary(r_tt_glm)
plot(r_tt_glm)
```

```{r}
r_fdr_glm <- glm(leaf~feret.diameter.ratio, data = r_all, family = gaussian())
summary(r_fdr_glm)
plot(r_fdr_glm)
```

```{r}
r_tap_glm <- glm(leaf~tooth.area.perimeter, data = r_all, family = gaussian())
summary(r_tap_glm)
plot(r_tap_glm)
```

```{r}
r_taip_glm <- glm(leaf~tooth.area.int.perimeter, data = r_all, family = gaussian())
summary(r_taip_glm)
plot(r_taip_glm)
```

```{r}
r_ata_glm <- glm(leaf~average.tooth.area, data = r_all, family = gaussian())
summary(r_ata_glm)
plot(r_ata_glm)
```

We ran a GLM for leaf number and tooth area:blade area.

```{r}
r_taba_glm <- glm(leaf~tooth.area.blade.area, data = r_all, family = gaussian())
summary(r_taba_glm)
plot(r_taba_glm)
```

```{r}
r_tp_glm <- glm(leaf~teeth.perimeter, data = r_all, family = gaussian())
summary(r_tp_glm)
plot(r_tp_glm)
```

```{r}
r_tip_glm <- glm(leaf~teeth.int.perimeter, data = r_all, family = gaussian())
summary(r_tip_glm)
plot(r_tip_glm)
```

```{r}
r_pa_glm <- glm(leaf~perimeter.area, data = r_all, family = gaussian())
summary(r_pa_glm)
plot(r_pa_glm)
```

```{r}
r_pr_glm <- glm(leaf~perimeter.ratio, data = r_all, family = gaussian())
summary(r_pr_glm)
plot(r_pr_glm)
```

```{r}
r_cp_glm <- glm(leaf~compactness, data = r_all, family = gaussian())
summary(r_cp_glm)
plot(r_cp_glm)
```

```{r}
r_sf_glm <- glm(leaf~shape.factor, data = r_all, family = gaussian())
summary(r_sf_glm)
plot(r_sf_glm)
```

```{r}
r_tba_glm <- glm(leaf~teeth.blade.area, data = r_all, family = gaussian())
summary(r_tba_glm)
plot(r_tba_glm)
```

We ran a GLM for leaf number and multiple variables. 
```{r}
r_clim_glm <- glm(leaf~feret.diameter.ratio + tooth.area.blade.area + teeth.blade.area + teeth.int.perimeter, data = r_all, family = gaussian())
summary(r_clim_glm)
plot(r_clim_glm)
```

We ran a GLM for leaf number and all variables. 
```{r}
r_all_glm <- glm(leaf~total.teeth + feret.diameter.ratio + tooth.area.perimeter + tooth.area.int.perimeter + average.tooth.area + tooth.area.blade.area + teeth.perimeter + teeth.int.perimeter + perimeter.area + perimeter.ratio + compactness + shape.factor + teeth.blade.area, data = r_all, family = gaussian())
summary(r_all_glm)
plot(r_all_glm)
beep(sound = 3, expr = NULL)
```
